Tracking p-adic precision: examples

### 2014-11-17 examples.tex
Changes for submission

Let $U$, $V$ and $W$ be three open subsets is some $K$-Banach spaces
$E$, $F$ and $G$ respectively. We assume that $0 \in U$, $0 \in V$ and
consider two locally analytic functions $f : U \to V$ and $g : V \to W$ 
two locally analytic functions around $0$. The composition $h = g \circ
f$ is then locally analytic around $0$ as well. Let us write the
analytic expansion of $f$, $g$ and $h$ as follows:
$$f = \sum_{n \geq 0} f_n, \quad 
g = \sum_{n \geq 0} g_n, \quad
h = \sum_{n \geq 0} h_n, \quad$$
where $f_n$, $g_n$ and $h_n$ are the restrictions to the diagonal of 
some $n$-linear forms $F_n$, $G_n$ and $H_n$ respectively. The aim of
this subsection is to prove the following proposition.

\begin{prop}
\label{prop:boundhr}
With the above notations, we have for all nonnegative integer $r$:
$$\Vert h_r \Vert \leq \sup_{m, (n_i)}
  \Vert g_m \Vert \cdot \Vert f_{n_1} \Vert \cdots \Vert f_{n_m} \Vert$$
where the supremum is taken over all couples $(m, (n_i))$ where $m$
is a nonnegative integer and $(n_i)_{1 \leq i \leq m}$ is a sequence of
length $m$ of nonnegative integers such that $n_1 + \ldots + n_m = r$.
\end{prop}

During the proof, multinomial coefficients will play an important role. 
We recall that they are defined as follows: 
given $s, k_1, \ldots, k_\ell$ some positive integers with $s \geq
k_1 + \cdots + k_\ell$, we set:
$$\binom s {k_1 \,\, k_2 \,\, \cdots \,\, k_\ell} =
  \frac{s!}{k_1!\: k_2! \cdots k_\ell! \: (s{-}k_1{-}\cdots{-}k_\ell)!}.$$
We also recall that these numbers are all positive integers.

We now expand $g \circ f$ as follows:
\begin{align}
g \circ f & = \sum_{m \geq 0} g_m \Big(\sum_{n \geq 1} f_n\Big) \nonumber \\
& = \sum \binom m {\!k_1 \,\, \cdots \,\, k_\ell\!} \:
G_m(f_{n_1}, \ldots, f_{n_1}, \ldots, f_{n_\ell}, \ldots, f_{n_\ell})
\label{eq:expansiongf}
\end{align}
where the latest sum runs over:

>>>>

Let $U$, $V$ and $W$ be three open subsets is some $K$-Banach spaces
$E$, $F$ and $G$ respectively. We assume that $0 \in U$, $0 \in V$ and
consider two locally analytic functions $f : U \to V$ and $g : V \to W$ 
around $0$. The composition $h = g \circ
f$ is then locally analytic around $0$ as well. Let us write the
analytic expansion of $f$, $g$ and $h$ as follows:
$$f = \sum_{n \geq 0} f_n, \quad 
g = \sum_{n \geq 0} g_n, \quad
h = \sum_{n \geq 0} h_n, \quad$$
where $f_n$, $g_n$ and $h_n$ are the restrictions to the diagonal of 
some $n$-linear forms $F_n$, $G_n$ and $H_n$ respectively. The aim of
this subsection is to prove the following proposition.

\begin{prop}
\label{prop:boundhr}
For any nonnegative integer $r$, 
\[
\Vert h_r \Vert \leq \sup_{m, (n_i)}
  \Vert g_m \Vert \cdot \Vert f_{n_1} \Vert \cdots \Vert f_{n_m} \Vert,
\]
where the supremum is taken over nonnegative integers $m$
and sequences $(n_i)_{1 \leq i \leq m}$ of nonnegative integers
with $n_1 + \cdots + n_m = r$.
\end{prop}

Multinomial coefficients will play an important role in the proof, so we recall their definition. 
Given positive integers $s, k_1, \ldots, k_\ell$ with $s \geq k_1 + \cdots + k_\ell$, set
\[
\binom s {k_1 \,\, k_2 \,\, \cdots \,\, k_\ell} =
  \frac{s!}{k_1!\: k_2! \cdots k_\ell! \: (s{-}k_1{-}\cdots{-}k_\ell)!}.
\]
These numbers are all positive integers.

We now expand $g \circ f$ as follows:
\begin{align}
g \circ f & = \sum_{m \geq 0} g_m \Big(\sum_{n \geq 1} f_n\Big) \nonumber \\
& = \sum \binom m {\!k_1 \,\, \cdots \,\, k_\ell\!} \:
G_m(f_{n_1}, \ldots, f_{n_1}, \ldots, f_{n_\ell}, \ldots, f_{n_\ell})
\label{eq:expansiongf}
\end{align}
where the second sum runs over
